Missing Data: Current Practice in Football Research and Recommendations for Improvement

### 2020-10-22 paper/paper.Rmd
edits

---
title: 'Missing data: Current practice in football research and recommendations for improvement'
bibliography: references.bib
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
---

@@

@@

aq_vis_miss <- vis_miss(data_plot_clean) + labs(tag = "A")
  #theme(text = element_text(size = 14))

aq_fct <- gg_miss_fct(data_plot_clean, team) + 
  #theme(text = element_text(size = 14)) +
  labs(x = "Team", y = "Variable", tag = "B") +
  theme(axis.text.x = element_text(size = 5))

gg_miss_scatter <- ggplot(data_plot_clean,
       aes(x = sprint_distance,
           y = sprints)) +
  geom_miss_point(size = 2) + 
  theme_minimal() +
  #theme(text = element_text(size = 14)) +
  labs(x = "Total sprint distance (m)", 
       y = "Number of sprints (count)", 
       colour = "",
       tag = "C")

aq_miss_var <- gg_miss_var(data_plot_clean) + labs(tag = "D")
```

>>>>

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for Improvement'
bibliography: references.bib
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
---

@@

Twitter: roberto_boberto

@@

aq_vis_miss <- vis_miss(data_plot_clean) + labs(tag = "(A)")
  #theme(text = element_text(size = 14))

aq_fct <- gg_miss_fct(data_plot_clean, team) + 
  #theme(text = element_text(size = 14)) +
  labs(x = "Team", y = "Variable", tag = "(B)") +
  theme(axis.text.x = element_text(size = 5))

gg_miss_scatter <- ggplot(data_plot_clean,
       aes(x = sprint_distance,
           y = sprints)) +
  geom_miss_point(size = 2) + 
  theme_minimal() +
  #theme(text = element_text(size = 14)) +
  labs(x = "Total sprint distance (m)", 
       y = "Number of sprints (count)", 
       colour = "",
       tag = "(C)")

aq_miss_var <- gg_miss_var(data_plot_clean) + labs(tag = "(D)")
```
